A state of the art end-to-end speech recognition algorithm with a homogenous structure.

### 2019-04-28 icml_2018_monolitic_end_to_end/doc/main.tex
Updates main file

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{tikz,placeins}
\usepackage{subcaption}
%\usepackage[caption = false]{subfig}
\usepackage{amssymb,amsmath,bm}
\usetikzlibrary{arrows,decorations.markings}
\tikzstyle{every picture}+=[font=\rmfamily\it\bfseries\large]

@@

\section{Structure of the Recurrent Sequence Recognizer}
\subsection{Review of the Room Simulator for Data Augmentation}
%
%
\begin{figure}
  \centering
    \begin{subfigure}{\linewidth}
      \centering
      \includegraphics[width=70mm]{room_diagram.eps}
      \caption{}
      \label{fig:room_diagram}
    \end{subfigure}
   \\
    \begin{subfigure}{\linewidth}
      \centering
      \includegraphics[width=70mm]{image_method.eps}
      \caption{}
      \label{fig:image_method}
    \end{subfigure}
    \caption{
    (a) A simulated room: There may be multiple microphones, a single target
    sound source, multiple noise sources in a cuboid-shape room with
    acoustically reflective walls. (b) A diagram showing the location
    of the real and the virtual sound sources assuming that the walls
    reflects acoustic wave like a mirror \cite{C_Kim_INTERSPEECH_2017_1}.}
  \vspace{-10mm}
\end{figure}
%
%
%
\subsection{Viterbi alignment and N-best alignment}

In conventional frame-wise CE-training, forced-alignment 
has been performed to obtain the frame-level acoustic unit  
boundaries. TODO(chanwcom) Even though the Viterbi algorithm
has advantages in simplicity and efficiency, it is based on
the conditional independence assumption.

>>>>

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{tikz,placeins}
\usepackage{subcaption}
\usepackage{algpseudocode}
%\usepackage[caption = false]{subfig}
\usepackage{amssymb,amsmath,bm}
\usetikzlibrary{arrows,decorations.markings}
\tikzstyle{every picture}+=[font=\rmfamily\it\bfseries\large]

@@

\subsection{Viterbi alignment and N-best alignment}

In conventional frame-wise CE-training, Viterbi alignment 
(a.k.a forced alignment) has been performed to obtain the frame-level 
acoustic unit  boundaries TODO(chanwcom). Even though the Viterbi algorithm
has advantages in simplicity and efficiency, it is based on
the conditional independence assumption.

In TFSC, we propose the following N-best alignment approach rather than
the Viterbi alignment algorithm to find the alignment information.

\begin{algorithmic}

\For {$m = 0, . . . , M-1$}
	\For {$l = 0, . . . , N_b-1$}
		\State {$\pi^{(l)}[m]$}
	\EndFor
\EndFor

\If {$i\geq maxval$}
    \State $i\gets 0$
\Else
    \If {$i+k\leq maxval$}
        \State $i\gets i+k$
    \EndIf
\EndIf
\label{algorithm:n_best_alignment}
\end{algorithmic}
